PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-13 paper/app-addmaterial.tex
Updated appendices
Appendix C
General revision

In this appendix, we collect some additional plots, in the same format of those
presented in figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV},
specifically: figure~\ref{fig:atlaszhighmass49fb-lowstat} is the same as
figure~\ref{fig:atlaszhighmass49fb}, but for a low-statistic MC run;
figure~\ref{fig:cmsdy2d11_bins12} is the same as
figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing lepton-pair
invariant mass bins,
$\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
$\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$;
and figure~\ref{fig:atlastop-rap} is the same as figure~\ref{fig:atlastop},
but for the distributions in the rapidity of the top quark, $y_{\mathrm{t}}$,
and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.

@@

%-------------------------------------------------------------------------------
\begin{figure}[!p]
    \centering
    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TRAP}%
    \caption{Same as figure~\ref{fig:atlastop}, but for the distributions
      in the rapidity of the top quark, $y_{\mathrm{t}}$, and in the rapidity of
      the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.}
    \label{fig:atlastop-rap}
\end{figure}
%-------------------------------------------------------------------------------

@@

Figure~\ref{fig:cmsdy2d11_bins12} demonstrates that the two bins at the
lowest invariant mass of the Drell--Yan lepton-pair measured by the CMS
experiment display very similar features as the bin at immediately larger
values of invariant mass, see figure~\ref{fig:cmsdy2d11_bins3456}: the EW
enhances the cross section (although of the order of 2\% -- 3\% across all the
rapidity range); the amount of this shift is slightly larger than the PDF
ucnertainty, but is largely overshot by the scale uncertainty; the MC\
uncertainty remains comparatively negligible.

>>>>

In this appendix, we collect some additional plots, in the same format of those
presented in figures~\ref{fig:atlaszhighmass49fb}-\ref{fig:cmsZ13TeV},
specifically: figure~\ref{fig:atlaszhighmass49fb-lowstat} is the same as
figure~\ref{fig:atlaszhighmass49fb}, but for a low-statistic MC run;
figure~\ref{fig:cmsdy2d11_bins12} is the same as
figure~\ref{fig:cmsdy2d11_bins3456}, but for the two missing lepton-pair
invariant mass bins,
$\SI{20}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{30}{\giga\electronvolt}$ and
$\SI{30}{\giga\electronvolt}<M_{\ell\bar\ell}<\SI{45}{\giga\electronvolt}$;
and figure~\ref{fig:atlastop-rap} is the same as figure~\ref{fig:atlastop},
but for the distributions in the rapidity of the top quark, $y_{\mathrm{t}}$,
and in the rapidity of the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$. In this
case the factorisation and renormalisation scales are kept equal to
$H_T/s$, see section~\ref{sec:toppair}.

@@

%-------------------------------------------------------------------------------
\begin{figure}[!p]
    \centering
    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TRAP}
    \includegraphics[width=0.46\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTRAP}\\
    \caption{Same as figure~\ref{fig:atlastop}, but for the distributions
      in the rapidity of the top quark, $y_{\mathrm{t}}$, and in the rapidity of
      the top-quark pair, $y_{\mathrm{t}\bar{\mathrm{t}}}$.}
    \label{fig:atlastop-rap}
\end{figure}
%-------------------------------------------------------------------------------

@@

Figure~\ref{fig:cmsdy2d11_bins12} demonstrates that the two bins at the
lowest invariant mass of the Drell--Yan lepton-pair measured by the CMS
experiment display very similar features as the bin at immediately larger
values of invariant mass, see figure~\ref{fig:cmsdy2d11_bins3456}: the EW
correction enhances the cross section by 2\% to 3\% across all the
rapidity range; the amount of this shift is slightly larger than the PDF
ucnertainty, but is largely overshot by the scale uncertainty; the MC\
uncertainty remains comparatively negligible.
